---
title: "2. Data Search and Discovery"
date: "`r Sys.Date()`"
output:
  html_vignette:
    fig_caption: false
vignette: >
  %\VignetteIndexEntry{3. Data Search and Discovery}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r knitr_options, echo=FALSE, results="hide"}
options(width = 120)
knitr::opts_chunk$set(results = "hold")
```

Searching for data within Dataverse is quite easy using the `dataverse_search()` function. The simplest searches simply consist of a query string:

```{r}
library("dataverse")
Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
dataverse_search("Gary King")[c("name")]
```

The results are paginated, so users can rely upon the `per_page` and `start` argument to requested subsequent pages of results. We'll start at 6 and to show that we retrieve the last five results from the previous query plus 15 more (due to `per_page = 20`):

```{r}
dataverse_search("Gary King", start = 6, per_page = 20)[c("name")]
```

More complicated searches can specify metadata fields like `title` and restrict results to a specific `type` of Dataverse object (a "dataverse", "dataset", or "file"):

```{r}
ei <- dataverse_search(author = "Gary King", title = "Ecological Inference", type = "dataset", per_page = 20)
# fields returned
names(ei)
# names of datasets
ei$name
```

Once datasets and files are identified, it is easy to download and use them directly in R. See the ["Data Retrieval" vignette](C-retrieval.html) for details.
