---
title: "3. Data Download"
date: "`r Sys.Date()`"
output:
  html_vignette:
    fig_caption: false
vignette: >
  %\VignetteIndexEntry{3. Data Download}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r knitr_options, echo=FALSE, results="hide"}
options(width = 120)
knitr::opts_chunk$set(results = "hold")
```

This vignette shows how to download data from Dataverse using the dataverse package. We'll focus on a Dataverse repository that contains supplemental files for [*Political Analysis Using R*](https://www.springer.com/gb/book/9783319234458), which is stored at Harvard's Dataverse Server <https://dataverse.harvard.edu>.

The Dataverse entry for this study is persistently retrievable by a "Digital Object Identifier (DOI)": https://doi.org/10.7910/DVN/ARKOTI and the citation on the Dataverse Page includes a "[Universal Numeric Fingerprint (UNF)](https://guides.dataverse.org/en/latest/developers/unf/index.html)": `UNF:6:+itU9hcUJ8I9E0Kqv8HWHg==`, which provides a versioned, multi-file hash for the entire study, which contains 32 files.


## Retrieving Metadata

We will download these files and examine them directly in R using the **dataverse** package. To begin, we need to loading the package and using the `get_dataset()` function to retrieve some basic metadata about the dataset:

```{r}
library("dataverse")
library("tibble") # to see dataframes in tidyverse-form
Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
```

The `get_dataset()` function lists all of the files in the dataset along with a considerable amount of metadata about each. (Recall that in Dataverse, `dataset` is a collection of files, not a single file.)  We can see a quick glance at these files using:

```r
dataset <- get_dataset("doi:10.7910/DVN/ARKOTI")
dataset$files[c("filename", "contentType")]
```

This shows that there are indeed 32 files, a mix of .R code files and tab- and comma-separated data files.

You can also retrieve more extensive metadata using `dataset_metadata()`:

```{r}
str(dataset_metadata("10.7910/DVN/ARKOTI"), 2)
```




## Retrieving Plain-Text Data

Now we'll get the corresponding data files. First, we retrieve a plain-text file like this dataset on electricity consumption by [Wakiyama et al. (2014)](https://doi.org/10.7910/DVN/ARKOTI/GN1MRT). Taking the file name and dataset DOI from this entry,

```{r, messages=FALSE}
energy <- get_dataframe_by_name(
  "comprehensiveJapanEnergy.tab",
  "10.7910/DVN/ARKOTI")

head(energy)
```

These `get_dataframe_*` functions, introduced in v0.3.0, directly read in the data into a R environment through whatever R function supplied by `.f`. The default of the  `get_dataframe_*` functions is to read in such data by `readr::read_tsv()`. The `.f` function can be modified to modify the read-in settings. For example, the following modification is a base-R equivalent to read in the ingested data.


```{r}
library(readr)
energy <- get_dataframe_by_name(
  "comprehensiveJapanEnergy.tab",
  "10.7910/DVN/ARKOTI",
  .f = function(x) read.delim(x, sep = "\t"))

head(energy)
```



## Retrieving Custom Data Fromats (RDS, Stata, SPSS)


If a file is displayed on dataverse as a `.tab` file like the survey data by [Alvarez et al. (2013)](https://doi.org/10.7910/DVN/ARKOTI/A8YRMP), it is likely that Dataverse [ingested](https://guides.dataverse.org/en/latest/user/tabulardataingest/index.html) the file to a plain-text, tab-delimited format.

```{r,  message=FALSE}
argentina_tab <- get_dataframe_by_name(
  "alpl2013.tab",
  "10.7910/DVN/ARKOTI")
```


However, ingested files may not retain important dataset attributes. For example, Stata and SPSS datasets encode value labels on to numeric values. Factor variables in R dataframes encode levels, not only labels. A plain-text ingested file will discard such information. For example,  the `polling_place` variable in this data is only given by numbers, although the original data labelled these numbers with informative values.

```{r}
str(argentina_tab$polling_place)
```

When ingesting, Dataverse retains a `original` version that retains these attributes but may not be readable in some platforms. The `get_dataframe_*` functions have an argument that can be set to `original = TRUE`. In this case we know that `alpl2013.tab` was originally a Stata dta file, so we can run:

```{r}
argentina_dta <- get_dataframe_by_name(
  "alpl2013.tab",
  "10.7910/DVN/ARKOTI",
  original = TRUE,
  .f = haven::read_dta)
```

Now we see that labels are read in through `haven`'s labelled variables class:

```{r}
str(argentina_dta$polling_place)
```



Users should pick `.f` and `original` based on their existing knowledge of the file. If the original file is a `.sav` SPSS file, `.f` can be `haven::read_sav`. If it is a `.Rds` file, use `readRDS` or `readr::read_rds`. In fact, because the raw data is read in as a binary, there is no limitation to the file types `get_dataframe_*` can read in, as far as the dataverse package is concerned.

There are two more ways to read in a dataframe other than `get_dataframe_by_name()`. `get_dataframe_by_doi()` takes in a file-specific DOI if Dataverse contains one such as <https://doi.org/10.7910/DVN/ARKOTI/IJPVOI>. This removes the necessity for users to set the `dataset` argument. `get_dataframe_by_id()` takes a numeric Dataverse identification number. This identifier is an internal number and is not prominently featured in the interface.


In addition to visual inspection, we can compare the UNF signatures for each dataset against what is reported by Dataverse to confirm that we received the correct files. (See the [UNF package](https://cran.r-project.org/package=UNF) and `unf` function).



## Retrieving Scripts and other files

If the file you want to retrieve is not data, you may want to use the  more primitive function, `get_file`, which gets the file data as a raw binary file. See the help page examples of `get_file()` that use the `base::writeBin()` function for details on how to write and read these binary files instead.

```{r, eval = FALSE}
code3 <- get_file("chapter03.R", "doi:10.7910/DVN/ARKOTI")
writeBin(code3, "chapter03.R")
```
