<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{Using UNF with The Dataverse Network}
-->

# Using UNF with The Dataverse Network #

This vignette shows some simple examples of how to use UNF signatures as part of a reproducible research workflow involving The Dataverse Network data archive. We'll start by loading some packages:

```{r}
library("UNF")
library("dvn")
```

## Retrieving Data from Dataverse ##

For the purposes of this section, we'll focus on one of the most-used data archives in Harvard University's [IQSS Dataverse Network](http://thedata.harvard.edu/dvn):

> John Y. Campbell; Yeung L. Chan; and Luis Viceira, 2007, "Replication data for: A Multivariate Model of Strategic Asset Allocation", http://hdl.handle.net/1902.1/QBXRSFLBQJ UNF:3:ZnYhHkZe2veTJAWaBDpPKA== The Harvard Dataverse Network [Distributor] V2 [Version]

This study is persistently retrievable by a "[Handle](http://en.wikipedia.org/wiki/Handle_System)": http://hdl.handle.net/1902.1/QBXRSFLBQJ. But in addition to the handle, the citation contains a study-level UNF signature: `UNF:3:ZnYhHkZe2veTJAWaBDpPKA==`, which provides a versioned, multi-file hash for the entire study, which contains three data files:

 * dataANN (`UNF:3:RVjeeV5JOY6jb8hJtk2T/A==`)
 * dataMTH_update (`UNF:3:TMiZOYj0Wdtq58sDBJjveQ==`)
 * dataQTR (`UNF:3:cTsOMQHb3efFo7i7pq6FfQ==`)

All of these UNFs indicate that the file- and study-level UNF signatures were generated using UNFv3 (an early version of the UNF algorithm).

While we can retrieve these files directly from a web browser via The Dataverse Network, we can also use the **dvn** package to retrieve these files and associated metadata programmatically. To retrieve all metadata associated with the study we simply do the following:

```{r}
xml <- dvMetadata("hdl:1902.1/QBXRSFLBQJ")
```

This returns a character string containing [DDI](http://www.ddialliance.org/)-formatted metadata about the entire study, including details on all of the files contained in the study. From the `xml` object, we can extract the set of files contained therein. This study contains numerous files, so we'll just look at the first few:

```{r}
files <- dvExtractFileIds(xml)
dim(files)
head(files[,-6], 6)
```

The first three files listed are the three datasets contained in the study collection. For any file, we can further extract information about the file formats available for download. Let's look at the `dataANN` dataset:

```{r}
dvDownloadInfo(files$fileId[1])
```

The data file is available in a number of formats, but is unfortunately protected by terms of use. As a result, it is not currently possible to download the data file directly without navigating to the study listing via a web browser.


Note: It is also possible to extract only metadata related to the data files in the study using the optional `include` argument to `dvMetadata`:

```
datadscr <- dvMetadata("hdl:1902.1/QBXRSFLBQJ", include="codeBook/dataDscr")
```


## Depositing Data in Dataverse ##

TBD
