<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{1. Introduction}
-->


# Introduction to Dataverse

The **dataverse** package is the official R client for [Dataverse 4](http://dataverse.org/) data repositories. The package enables data search, retrieval, and deposit with any Dataverse installation, thus allowing R users to integrate public data sharing into the reproducible research workflow.

In addition to this introduction, the package contains three additional vignettes covering:

  * [Data Search](search.html)
  * [Data retrieval](retrieval.html)
  * [Data archiving](archiving.html)

They can be accessed from [CRAN](https://cran.r-project.org/package=dataverse/index.html) or from within R using `vignettes(package = "dataverse")`.

The dataverse client package can be installed from [CRAN](https://cran.r-project.org/package=dataverse), and you can find the latest development version and report any issues on GitHub:

```R
if (!require("ghit")) {
    install.packages("ghit")
}
ghit::install_github("iqss/dataverse-client-r")
library("dataverse")
```

(Note: **dataverse** is the next-generation iteration of [the **dvn** package](https://cran.r-project.org/package=dvn), which works with Dataverse 3 ("Dataverse Network") applications. See the appendix of this vignette for a cross-walk of functionality between **dvn** and **dataverse**.)

## Quick Start

Dataverse has some terminology that is worth quickly reviewing before showing how to work with Dataverse in R. Dataverse is an application that can be installed in many places. As a result, **dataverse** can work with any instllation but you need to specify which installation you want to work with. This can be set by default with an environment variable, `DATAVERSE_SERVER`:

```{r}
library("dataverse")
Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
```

This should be the Dataverse server, without the "https" prefix or the "/api" URL path, etc. The package attempts to compensate for any malformed values, though. 

Within a given Dataverse installation, organizations or individuals can create objects that are also called "Dataverses". These Dataverses can then contain other *dataverses*, which can contain other *dataverses*, and so on. They can also contain *datasets* which in turn contain files. You can think of Harvard's Dataverse as a top-level installation, where an institution might have a *dataverse* that contains a subsidiary *dataverse* for each researcher at the organization, who in turn publishes all files relevant to a given study as a *dataset*.

You can search for and retrieve data without a Dataverse account for that a specific Dataverse installation. For example, to search for data files or datasets that mention "ecological inference", we can just do:

```{r}
dataverse_search("ecological inference")
```

The [search vignette](search.html) describes this functionality in more detail. To retrieve a data file, we need to investigate the dataset being returned and look at what files it contains using a variety of functions, the last of which - `get_file()` - can retrieve the files as raw vectors:

```R
get_dataset()
dataset_files()
get_metadata()
get_file()
```

For "native" Dataverse features (such as user account controls) or to create and publish a dataset, you will need an API key linked to a Dataverse installation account. Instructions for obtaining an account and setting up an API key are available in the [Dataverse User Guide](http://guides.dataverse.org/en/latest/user/account.html). (Note: if your key is compromised, it can be regenerated to preserve security.) Once you have an API key, this should be stored as an environment variable called `DATAVERSE_KEY`. It can be set within R using: 

```R
Sys.setenv("DATAVERSE_KEY" = "examplekey12345")
```

With that set, you can easily create a new dataverse, create a dataset within that dataverse, push files to the dataset, and release it:

```R
# create a dataverse
dat <- create_daverse("mydataverse")

# create a list of metadata
metadat <- list(title = "My Study",
                creator = "Doe, John",
                description = "An example study")

# create the dataset
dat <- initiate_dataset("mydataverse", body = metadat)

# add files to dataset
tmp <- tempfile()
write.csv(iris, file = tmp)
f <- add_file(dat, file = tmp)

# publish new dataset
publish_dataset(dat)
```

Your data are now publicly accessible.


## Appendix: dvn to dataverse Crosswalk

The original [dvn](https://cran.r-project.org/?package=dvn) package provided functionality for searching, retrieving, and depositing data. Here is a cross-walk of functionality in case you were already familiar with the dvn package:

| API Category | **dataverse** functions | **dvn** functions |
| ------------ | ----------------------- | ----------------- |
| Data Search | `dataverse_search()` | `dvSearch()` |
| Data Retrieval | `get_metadata()` | `dvMetadata()` |
|| `get_file()` |  |
| Data Deposit | `create_dataverse()` |  |
|| `initiate_dataset()` | `dvCreateStudy()` |
|| `update_dataset()` | `dvEditStudy()` |
|| `add_file()` | `addFile()` |
|| `delete_file()` | `dvDeleteFile()` |
|| `publish_sword_dataset()` | `dvReleaseStudy()` |
|| `delete_sword_dataset()` |  |
|| `service_document()` | `dvServiceDoc()` |
|| `dataset_statement()` | `dvStudyStatement()` |
|| `list_datasets()` | `dvUserStudies()` |

